---
title: "Scheduled_Price Tracker - Shiny App"
author: "28Melvin"
date: "2021/02/01"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    theme: paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Melvin There!

Github: Yet to [Scheduled_Price Tracker Github](https://github.com/28Melvin/Scheduled_PriceTracker) \
Shinyapps.io: [Scheduled_Price Tracker ShinyApp](https://melvin28.shinyapps.io/ScheduledTracker) 

This is similar to the RShiny App:  [Price Tracker](https://melvin28.shinyapps.io/PriceTracker) \

The only difference is that the user cannot load the prices of the products but I use a chronjob (windows: TaskScheduler) to 
scrape the price, as well as store the prices in a databse. The user can only load the prices from the remote database and plot the price development. 

Therefore only the structure of the files is different from the previous mentioned app. 

General Structure: 

2 .R files
   - app.R
   - global.R
   - ScheduleScraper.R

1 .Renviron file
  - .Renviron
  
All three files are uploaded to shinyapps.io where the app is pusblished. Data is stored in a remote MySQL database. 


# The global.R file

```{r, eval=FALSE}


# table name of database
table1 <- "ScheduledTracker"

loadData <- function(){
  
  # connect to the database
  db <- dbConnect(MySQL(), dbname = Sys.getenv("databaseName1"), 
                  host = Sys.getenv("host1"),  
                  port = as.integer(Sys.getenv("port1")), 
                  user =  Sys.getenv("user1"), 
                  password = Sys.getenv("password1")) 
  
  # construct the fetching query 
  
  query <- sprintf("SELECT * FROM %s", table1)
  
  # Submit the fetch query and disconnect
  
  data <- dbGetQuery(db, query)
  
  dbDisconnect(db)
  
  
  return(data)
  
}


plotAirPods <- function(input){
  
  
  input1 <- input[which(input[,"ProductName"] == "AirPods mit Ladecase"),]
  #prepare data
  ggplot(data = input1, aes(x = YearMonthDate, y = Price, group = 1)) + geom_line()
  
  
}

plotIPhone <- function(input){
  
  input1 <- input[which(input[,"ProductName"] == "Apple IPhone 12 Pro 256 GB"),]
  
  ggplot(data = input1, aes(x = YearMonthDate, y = Price, group = 1)) + geom_line()
  
}





```

# The app.R File


```{r, eval=FALSE}
# r-shiny project
library(shiny) 
library(RMySQL)
library(ggplot2)

source("./global.R")


# Define UI / Layout 
# fluidpage -> function
ui <- fluidPage(
  
  titlePanel("Prices"),
  

  
  sidebarLayout(
    
    sidebarPanel("Choose the product you wish to get the price for: ", 
                 
                 br(),
                 br(),
                 selectInput("productID","Choose product: ", c("Apple IPhone 12 Pro 256 GB", "AirPods mit Ladecase")),
                 br(),
                 br(),
                 actionButton("plotData", "Plot Data"),
                 br(), 
                 h1(textOutput("currentPrice"), align = "center")), 
                 
               
    
    mainPanel("Prices over Time", tabsetPanel(type = "tabs", 
                          tabPanel("IPhone 12 Pro - 256 GB", plotOutput("plotIPhone")),
                          tabPanel("AirPods mit Ladecase", plotOutput("plotAirPods"))),
              
              position = "left" #sidebar position
              
         
        
  ))
  
)


# Define server logic required 
server <- function(input, output) {
  
  
  # if the user pushes the "Get newest Price" Button - newest price is extracted 
  # and written to remote database + shown below the button 
  observeEvent(input$plotData, {
    
    
    tableInput <- loadData()
    
    if(input$productID == "Apple IPhone 12 Pro 256 GB"){
      
      output$plotIPhone <- renderPlot(plotIPhone(tableInput))
      
    }
    else
    {
    
     output$plotAirPods <- renderPlot(plotAirPods(tableInput))
    }
    
   # output$datas <- renderTable(tableInput)
    
    
  })
  
  
}


# run the app 
shinyApp(ui = ui, server = server)



```

# The .Renviron File

The following should be included in the .Renviron file. The .Renviron file should also be uploaded to the shinyapps.io server. 
When testing the app locally I used the: usethis::edit_r_environ("projects") command to create the .Renviron file. 
```{r, eval= FALSE}


host1 = put_the_host_here
port1 = put_port_here
user1 = put_user_here
password1 = put_password_here
databaseName1 = put_databaseName_here
table1 = put_tableName_here

```

# The ScheduleScraper.R File

```{r, eval = FALSE}

############################################################################
#
# 1. Functions for extracting the prices 
# 2. database access / save data to database 


# Part of an R Project - Renviron file was created using: 

# usethis::edit_r_environ("project")


# 3. The loading of the data happens in the RShiny app and not in the cronjob!
##
#
# necesseary libraries
library(xml2)  
library(rvest)
library(stringr)
library(lubridate)

library(ggplot2)

library(RMySQL)
# 1. price extraction 


getIPhone <- function(){
  
  #product_ipad <-  "_apple-ipad-air-wi-fi-2020-2686182.html"
  #ipad <-  gsub(" ", "",paste(base_url,product_ipad))
  
  getSite_iphone <- read_html("https://www.apple.com/de/shop/buy-iphone/iphone-12-pro/6,1%22-display-256gb-graphit")
  
  getPrice <- getSite_iphone %>%
    html_nodes("span.as-price-currentprice") %>%  #span = tag name, as-price-currentprice = class name
    html_text()
  getPrice <- str_remove_all(getPrice, "[\n]") # € macht Probleme mit Codierung, daher hier rausgenommen und im str_replace_all mit Berücksichtigung
  getPrice <- gsub(" ","", getPrice)
  getPrice <- gsub(".","",getPrice, fixed=TRUE) #fixed=TRUE so that only the "." is replaced
  getPrice <- str_replace_all(getPrice, ",\\w+", "") #remove all character after "," included
  getPrice <- substr(getPrice, 1,nchar(getPrice)-1)
  getPrice_iphone <- as.integer(getPrice)
  
  
  
  return(getPrice_iphone)
}



getAirPod <- function(){
  
  getSite_airpod <- read_html("https://www.apple.com/de/shop/product/MV7N2ZM/A/airpods-mit-ladecase")
  
  getPrice <- getSite_airpod %>%
    html_nodes("span.current_price") %>%
    html_text()
  
  
  getPrice <- str_remove_all(getPrice, "[\n]") # € macht Probleme mit Codierung, daher hier rausgenommen und im str_replace_all mit Berücksichtigung
  getPrice <- gsub(" ","", getPrice)
  getPrice <- str_replace_all(getPrice, ",\\w+", "") #remove all character after "," included
  getPrice <- substr(getPrice, 1,nchar(getPrice)-1)
  getPrice_airpod <- as.integer(getPrice)
  
  return(getPrice_airpod)
  
}


getTime <- function(){
  
  
  YearMonthDate <- Sys.Date()
  Year <- year(YearMonthDate)
  inputtable <- as.data.frame(cbind(Year,YearMonthDate))
  inputtable$YearMonthDate <-  as.numeric(inputtable$YearMonthDate)
  inputtable$YearMonthDate <- format(as.Date(inputtable$YearMonthDate, origin="1970-01-01"), "%Y:%m:%d")
  
  return(inputtable)
  
  # result is a table that is then later combined with the product prices to be stored in 
  # the mysql database 
  
  
}


# 2. Database access and save

####################
table1 <- "ScheduledTracker"
####################

# credentials in the 
# usethis::edit_r_environ file

saveData <- function(data){
  
  #connect to database
  
  db <- dbConnect(MySQL(), dbname = "web140_db2",  
                  host = "server26.webgo24.de",  
                  port = as.integer("3306"), 
                  user = "web140",  
                  password = "Target48!")

  #######################################################################################
  
  
  # construct update query by looping over the data fields
  
  query <- sprintf(
    "INSERT INTO %s (%s) VALUES ('%s')", 
    
    table1, # 
    paste(names(data), collapse = ", "),
    paste(data, collapse = "', '")    
    
  )
  
  # Submit the update query and disconnect
  
  dbGetQuery(db, query)
  
  dbDisconnect(db)
  
}


ProductName <- "Apple IPhone 12 Pro 256 GB"
Price <- getIPhone()
times1 <- getTime()

row1 <- as.data.frame(cbind(ProductName, Price, times1))

saveData(row1)

ProductName <- "AirPods mit Ladecase"
Price <- getAirPod()
times2 <- getTime()

row2 <- as.data.frame(cbind(ProductName, Price, times2))

saveData(row2)

```

# The chronjob / Windows Task Scheduler

I only want to provide the input I used for the action tab in the task scheduler

```{r, eval=FALSE}

Programm/Script: "C:\\Program Files\\R\R-4.0.3\\bin\\Rscript.exe"
arguments: "C:\\Users\\NotYetDecided\\Desktop\\git\\RProjects\\ShinyApps\\ScheduledTracker\\ScheduleScraper.R"

```
